Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-31 paper/paper.tex
adding discussion section and one par on it

The overarching goal of our study is to identify the ability of simple
techniques to find bugs in \js\ engines with cross-engine differential
testing.  We analyzed the impact of two orthogonal dimensions in this
study: test mining and fuzzing. The first dimension focuses on the
impact of inputs, mined from the web, in bug finding whereas the
second dimension focuses on the impact of fuzzing these inputs.

@@

\Igor{
  Apos este experimento, foram obtidos \nofuzzAll{} buckets sendo destes \nofuzzHITotal

@@

>>>>

The overarching goal of our study is to identify the ability of
cross-engine differential testing to find bugs in \js\ engines.  We
analyzed the impact of two orthogonal dimensions in this study: test
mining and fuzzing. The first dimension focuses on the impact of
inputs, mined from the web, in bug finding whereas the second
dimension focuses on the impact of fuzzing these inputs.

@@

\Igor{
  Neste experimento, obtemos \nofuzzAll{} buckets distintos, a proporcao \'e de 
  \nofuzzHITotal{} HI e apenas \nofuzzLOTotal{} LO. Como descrito anteriormente,
  n\'os analisamos e discutimos se estas discrepancias reportadas pela ferramenta sao 
  casos de bugs reais ou casos de falso positivos.
  Nesta analise, nos observamos que cerca de \Fix{63} buckets sao duplicados, ou seja,
  estes warnings foram reportados anteriormente nos issues trackers dos engenhos 
  ou podem ser encontrados casos similares em buckets distintos. Um exemplo claro dos 
  buckets duplicados podem ser encontrados atraves dos testes da suite Test262,
  onde esta suite cobre as especificacoes da linguagem em arquivos distintos e que
  podem conter mensagens de erro diferentes.

@@

\section{Discussion}

It is important to highlight that our treatment on both dimensions of
analysis--test mining and fuzzing--could be improved by selecting more
test cases or using more advanced fuzzing tools. The main rationale is
that if these techinques perform well with the objects we used
(Section~\ref{sec:methodology}) then the approach would perform even
better with more elaborate objects.

\Fix{...}
